Learning STRIPS action models with classical planning

### 2017-10-06 doc/icaps-18/strips-learning.tex
addded optimization to the compiler

Given a learning task $\Lambda''=\tup{\Psi,\Sigma}$ the compilation outputs a classical planning task $P_{\Lambda''}=\tup{F_{\Lambda''},A_{\Lambda''},I_{\Lambda''},G_{\Lambda''}}$ such that:
\begin{itemize}
\item $F_{\Lambda''}$ extends $F$ with:
\begin{itemize}
\item Fluents representing the programmed action model ($pre_f(\xi)$, $del_f(\xi)$ and $add_f(\xi)$ for every $f\in F_v$ and $\xi \in \Xi$). If a fluent $pre_f(\xi)/del_f(\xi)/add_f(\xi)$ holds, it means that $f$ is a precondition/negative effect/positive effect of the operator $\xi$. 
\item Fluents $\{test_t\}_{1\leq t\leq \tau}$, indicating the example where the programmed model is being validated.
\item Fluents $mode_{pre}$, $mode_{eff}$ and $mode_{val}$ indicating whether the preconditions of the action schema are being programmed, the effects of the action schema are being programmed or the programmed action models are being validated.
\end{itemize}
\item $I_{\Lambda''}$, contains the fluents from $F$ that encode $s_0^1$ (i.e. the initial state of the first learning example), every fluent $pre_f(\xi)\in F_{\Lambda}$ (initially all operators have all the possible preconditions) and $mode_{pre}$. 
\item $G_{\Lambda''}=\{test_t\}$,{\small $1\leq t\leq \tau$}, indicates that the programmed action model is validated in all the learning examples.
\item $A_{\Lambda''}$ contains actions of three different types:
\begin{enumerate}
\item The actions for programming the operator schema. This includes the actions for removing a {\em precondition} $f\in F_v$ from the action schema $\xi\in\Xi$.

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{programPre_{f,\xi}})=&\{pre_{f}(\xi),mode_{pre}, \\
&\neg mode_{eff}, \neg mode_{val}\},\\    
\cond(\mathsf{programPre_{f,\xi}})=&\{\emptyset\}\rhd\{\neg pre_{f}(\xi)\}.
\end{align*}
\end{small}

@@

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{programEff_{f,\xi}})=&\{\neg del_{f}(\xi),\neg add_{f}(\xi),\\                                                   
&\neg mode_{val}\},\\
\cond(\mathsf{programEff_{f,\xi}})=&\{pre_{f}(\xi)\}\rhd\{del_{f}(\xi)\},\\
&\{\neg pre_{f}(\xi)\}\rhd\{add_{f}(\xi)\},\\
&\{mode_{pre}\}\rhd\{\neg mode_{pre},mode_{eff}\}.
\end{align*}
\end{small}

\item The actions for applying an already programmed operator schema $\xi\in\Xi$ bounding it with objects $\omega\subseteq\Omega^{ar(\xi)}$
\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{apply_{\xi,\omega}})=&\{pre_{f}(\xi)\implies p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
\cond(\mathsf{apply_{\xi,\omega}})=&\{del_{f}(\xi)\}\rhd\{\neg p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{add_{f}(\xi)\}\rhd\{p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{mode_{pre}\}\rhd\{\neg mode_{pre},mode_{val}\},\\
&\{mode_{eff}\}\rhd\{\neg mode_{eff},mode_{val}\}.
\end{align*}
\end{small}

>>>>

Given a learning task $\Lambda''=\tup{\Psi,\Sigma}$ the compilation outputs a classical planning task $P_{\Lambda''}=\tup{F_{\Lambda''},A_{\Lambda''},I_{\Lambda''},G_{\Lambda''}}$ such that:
\begin{itemize}
\item $F_{\Lambda''}$ extends $F$ with:
\begin{itemize}
\item Fluents representing the programmed action model ($pre_f(\xi)$, $del_f(\xi)$ and $add_f(\xi)$ for every $f\in F_v$ and $\xi \in \Xi$). If a fluent $pre_f(\xi)/del_f(\xi)/add_f(\xi)$ holds, it means that $f$ is a precondition/negative effect/positive effect of the operator $\xi$. 
\item Fluents $\{test_t\}_{1\leq t\leq \tau}$, indicating the example where the programmed model is being validated.
\item Fluents $mode_{prog}$ and $mode_{val}$ indicating whether the operator schema are being programmed or the programmed operators are being validated.
\end{itemize}
\item $I_{\Lambda''}$, contains the fluents from $F$ that encode $s_0^1$ (i.e. the initial state of the first learning example), every fluent $pre_f(\xi)\in F_{\Lambda}$ (initially all operators have all the possible preconditions) and $mode_{prog}$. 
\item $G_{\Lambda''}=\{test_t\}$,{\small $1\leq t\leq \tau$}, indicates that the programmed action model is validated in all the learning examples.
\item $A_{\Lambda''}$ contains actions of three different types:
\begin{enumerate}
\item The actions for programming the operator schema. This includes the actions for removing a {\em precondition} $f\in F_v$ from the action schema $\xi\in\Xi$.

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{programPre_{f,\xi}})=&\{pre_{f}(\xi),\neg del_{f}(\xi),\neg add_{f}(\xi),\\
& mode_{prog}\},\\    
\cond(\mathsf{programPre_{f,\xi}})=&\{\emptyset\}\rhd\{\neg pre_{f}(\xi)\}.
\end{align*}
\end{small}

@@

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{programEff_{f,\xi}})=&\{\neg del_{f}(\xi),\neg add_{f}(\xi),\\                                                   
& mode_{prog}\},\\ 
\cond(\mathsf{programEff_{f,\xi}})=&\{pre_{f}(\xi)\}\rhd\{del_{f}(\xi)\},\\
&\{\neg pre_{f}(\xi)\}\rhd\{add_{f}(\xi)\}.
\end{align*}
\end{small}

\item The actions for applying an already programmed operator schema $\xi\in\Xi$ bounding it with objects $\omega\subseteq\Omega^{ar(\xi)}$
\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{apply_{\xi,\omega}})=&\{pre_{f}(\xi)\implies p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
\cond(\mathsf{apply_{\xi,\omega}})=&\{del_{f}(\xi)\}\rhd\{\neg p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{add_{f}(\xi)\}\rhd\{p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{mode_{prog}\}\rhd\{\neg mode_{prog},mode_{val}\}.
\end{align*}
\end{small}
